Finite Property Convex Elicitation Paper

### 2019-01-21 jessie-writeup/jw-holes-clarified.tex
Added thoughts and updates to my writeup... still incomplete

\begin{notation}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.
\end{notation}

%\begin{definition}
%	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
%	Let $\gamma$ and $\zeta$ be set-valued properties.
%	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
%\end{definition}

%Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
%\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. %there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\jessie{Assumptions used: Finite FDLS}

	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{Double check/clarify the statement of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.

@@

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\Gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. \jessie{Waved my hands at the bijection bit, come back and clarify.}
	Therefore, the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}

@@

\item [$1 \implies 5$]
We know $\strip(\gamma) = \trim(\Gamma)$, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\end{enumerate}

@@

\begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convexity?} affine loss $A: \R \times \P \to \reals$ be given.
	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
\end{theorem}

>>>>

\begin{notation}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.

\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$''}
\end{notation}
\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. 
\end{definition}

We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
\jessiet{Do we want the above statement?}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{Double check/clarify the statement of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.
	(This can also be seen by the closure of level sets that union to the simplex.)

@@

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. 
	As the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).

  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
  \item $\trim(\Gamma)$ is finite. \jessie{IMO, we can cut given the next point}
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}

@@

\item [$1 \implies 5$]
We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\item[$2 \implies 1$]
\jessie{Only needed if we decide to cut 3 and 4.}
$\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists} is an embedding of $\Gamma$.
\end{enumerate}

@@

\begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convex elicitability? I read $\Gamma$-regular to mean that $L(r,p) < \infty$ for all $r \in \R$.} affine loss $L: \R \times \P \to \reals$ be given.
	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
\end{theorem}

\begin{conjecture}
A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
\end{conjecture}
\begin{proof}

\begin{enumerate}
\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
\item[$\impliedby$] A convex set of positive measure contains the ball, which is a superset of a convex hull of affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
\end{enumerate}
\end{proof}
